---
title: "Temporality and disruption of routines"
author: "Julian Barg"
date: "March 27, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(lubridate)
library(feather)
```

## 1. Temporality literature

Identified as import issue in many research streams:

> - Temporality and sustainability (Bansal & DesJardine 2014)
> - Agent's temporal orientation (Wowak et al. 2015)
> - Decision speed (Kwnatzki et al. 2013)

## 2. Researching "pace"

> - At what pace (frequency) are changes made?
> - Is a company moving slow or moving fast?
> - A focus on the content of decisions can obscure the issue of how decisions are received.

##{.flexbox .vcenter}

<b>
For instance, a company that changes a policy 5x in one year could only be sure that there is confusion and volatility.
</b>

## 3. Why it matters

> - Often focus in literature on the regular, steady processes
>   - E.g, exclusion of crisis years, "abnormal" industries from modeling
> - Irregular events can have unequally big effect on outcome measure
>     - E.g., performance (insert your own example)
>     - In sustainability: environmental impacts of disasters
>     - E.g., deepwater horizont oil spill
>         - Spilling a couple of barrels every now and then during regular operations
>         - 4.9 million barrels in one event
> - Prevent disasters, rather than optimizing regular operations

## 4. Modeling approaches (in theory)

Internal vs. external perspective

> - Internal
>     - Impression management
>     - Intention vs effects "on the ground"
> - External
>     - Challenge: lack of introspective

## 4. Modeling approaches: data

> - M&As 
> - <div class="red2"><b>Turnover</b></div>
>     - Cause of changes (leadership change)
>     - Symptom of changes (layoffs)
> - Media perspective (external)

## 4. Modeling approaches: the challenge

> - Model change as a cumulative phenomenon
> - How do we conceptualize instability as a quantitative phenomenon?

## 5. Outcome variables

> - Industrial disasters
> - <div class="red2"><b>Product recalls</b></div>
> - Conventional performance measures

## 6. Data: sample{.smaller}

```{r companies, echo=TRUE, warning=FALSE}
sample <- read_feather('../sample 2019-03-16.feather')
unique(sample$name)
```

## 6. Data: recalls{.smaller}

```{r recalls, echo=TRUE, message=FALSE, warning=FALSE}
cpsc <- read_csv("../downloads/cpsc.csv")
cpsc$date <- mdy(cpsc$date)
cpsc %>%
  ggplot(aes(x=date)) + geom_histogram() + labs(title = "Histogram of recalls", x="Time", y=element_blank())
``` 

---

```{r hist_cpsc_focus, echo=TRUE, message=FALSE}
cpsc %>%
  filter(.$date >= date("2005-01-01")) %>%
  ggplot(aes(x=date)) + geom_histogram() + 
  labs(title = "Histogram of recalls", x="Time", y=element_blank())
```

## 6. Data: turnover I{.smaller}

```{r time_trend, warning=FALSE, echo=TRUE}
sample %>%
  ggplot(aes(x = year)) + geom_bar() + labs(title = 'Observations (executives) per year') + 
  scale_x_continuous(breaks = seq(2009, 2018, by = 1))
```

---

```{r tenure, echo=TRUE}
sample %>% group_by(execid) %>% summarize(n = n()) %>%
  ggplot(aes(x=n)) + geom_bar() + labs(title='Histogram of tenure of executives') + 
  scale_x_continuous(breaks = seq(0, 10, by=1))
```

## References
- Bansal, P., & DesJardine, M. (2014). Business sustainability: It is about time. Strategic Organization, 12(1), 70–78. https://doi.org/10.1177/1476127013520265
- Kownatzki, M., Walter, J., Floyd, S. W., & Lechner, C. (2013). Corporate Control and the Speed of Strategic Business Unit Decision Making. Academy of Management Journal, 56(5), 1295–1324. https://doi.org/10.5465/amj.2011.0804
- Wowak, A. J., Mannor, M. J., & Wowak, K. D. (2015). Throwing Caution to the Wind: The Effect of CEO Stock Option Pay on the Incidence of Product Safety Problems. Strategic Management Journal, 36(7), 1082–1092. https://doi.org/10.1002/smj.2277

