---
title: "4. Explore recalls"
author: "Julian Barg"
date: "April 16, 2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document is deployed at https://julianbarg.shinyapps.io/4_-_Explore_recalls/.

```{r imports}
library(tidyverse)
library(ggvis)
```

## Read data

```{r read}
library(feather)
recalls_matched <- read_feather('shiny_data/recalls_matched 2019-04-19.feather')

colnames(recalls_matched)
```

## Visualize recalls per company

### Grab recalls only
```{r recalls_only}
recalls <- select(recalls_matched, name, year, recalls)
recalls <- unique(recalls)
glimpse(recalls)
```

```{r see_nas}
sum(is.na(recalls$recalls))
```

### Visualize recalls by company
```{r select_company}
selectInput("company", "Company:",
            choices = unique(recalls$name), 
            selected = unique(recalls$name)[1])
```

```{r render}
reactive({
  recalls %>%
    filter(name == input$company) %>%
    filter(year > 2010) %>%
    ggvis(~year, ~recalls) %>%
    layer_points() %>%
    add_axis("x", title = "Year") %>%
    add_axis("y", title = "Recalls") %>%
    bind_shiny('plot')
})

ggvisOutput('plot')
```

Although plenty of companies do not have any nonzero observations, there should be enough cases with variance left to allow for a statistical analysis.

## Other exploration

### Observations per year
```{r by_year}
recalls %>%
  group_by(year) %>%
  summarize(n = sum(recalls))
```

Because our dataset does not have good quality data for the years 2008-2010, we are going to run our analysis based on the years 2011-2017. We might be able to rectify this problem later by adjusting the spider that we scrape the CPSC with.

```{r distribution_year, fig.width=10, fig.height=16}
recalls %>%
  filter(year > 2010) %>%
  ggplot(aes(x=recalls)) +
  facet_grid(vars(year)) +
  geom_bar()
```

### Find outliers
```{r outliers}
recalls[recalls$recalls > 8, ]
```

The outliers are almost all from the same companies, Home Depot and Target. So if we consider in our final model only the change per year, we don't need to be concerned about excessive levarage of those observations.

### Find observations with no variance

```{r num_companies}
length(unique(recalls$name))
```

```{r non_zero}
recalls %>%
  group_by(name) %>%
  summarize(max = max(recalls)) %>%
  filter(max == 0)
```

19 out of the 39 remaining observations only have non-zero values, leaving us with only 20 observations (companies) with variance.