---
title: "4. Explore recalls"
author: "Julian Barg"
date: "April 16, 2019"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r imports}
library(tidyverse)
library(ggvis)
```

This document is deployed at https://julianbarg.shinyapps.io/4_-_Explore_recalls/.

## Read data

```{r read}
library(feather)
recalls_matched <- read_feather('shiny_data/recalls_matched 2019-04-17.feather')

colnames(recalls_matched)
```

## Missing data

### Print missing data
```{r na}
recalls_matched[is.na(recalls_matched$year), ]
```

### See all entries for those companies
```{r na_all}
missing <- c('003054', '007127', '009563')
recalls_matched[recalls_matched$gvkey %in% missing, ]
```

### Drop missings
The observations for these entries seem to be missing completely. It seems their upper management was not tracked by Compustat. For now, we will remove these completely.

```{r na_remove}
recalls_matched <- recalls_matched[!(recalls_matched$gvkey %in% missing), ]
length(unique(recalls_matched$name))
```

## Visualize recalls per company

### Grab recalls only
```{r recalls_only}
recalls <- select(recalls_matched, name, year, recalls)
recalls <- unique(recalls)
glimpse(recalls)
```

### Fill NA with 0
The NA means no recalls were found, and no executives/upper management is present. So its not incorrect to fill them with 0 for no recalls for the purpose of our visualization.
```{r spread}
recalls <- spread(recalls, name, recalls)
recalls[is.na(recalls)] <- 0
recalls <- gather(recalls, "name", "recalls", -year)
glimpse(recalls)
```

### Visualize recalls by company
```{r select_company}
selectInput("company", "Company:",
            choices = unique(recalls$name), 
            selected = unique(recalls$name)[1])
```

```{r render}
reactive({
  recalls %>%
  filter(name == input$company) %>%
    ggvis(~year, ~recalls) %>%
    layer_points() %>%
    add_axis("x", title = "Year") %>%
    add_axis("y", title = "Recalls") %>%
    bind_shiny('plot')
})

ggvisOutput('plot')
```

Although plenty of companies do not have any nonzero observations, there should be enough cases with variance left to allow for a statistical analysis.

## Other exploration

### Observations per year
```{r by_year}
recalls %>%
  group_by(year) %>%
  summarize(n = sum(recalls))
```

```{r distribution_year, fig.width=10, fig.height=16}
recalls %>%
  ggplot(aes(x=recalls)) +
  facet_grid(vars(year)) +
  geom_bar()
```

### Find outliers
```{r outliers}
recalls[recalls$recalls > 8, ]
```

The outliers are almost all from the same companies, Home Depot and Target. So if we consider in our final model only the change per year, we don't need to be concerned about excessive levarage of those observations.

### Find observations with no variance
```{r non_zero}
recalls %>%
  group_by(name) %>%
  summarize(max = max(recalls)) %>%
  filter(max == 0)
```

18 out of the 39 remaining observations only have non-zero values, leaving us with only 21 observations (companies) with variance.