---
title: "5. Preprocessing merged data"
author: "Julian Barg"
date: "April 17, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r tidy}
library(tidyverse)
```

## Read data

```{r read}
library(feather)
recalls_matched <- read_feather("../preprocessed/recalls_matched 2019-04-21.feather")

personnel <- select(recalls_matched, gvkey, name, execid, year, personnel_is_ceo, personnel_full_name)

glimpse(personnel)
```

## Check the data

### Check for duplicates

Are there duplicate entries, for instance in a year if an employee becomes a CEO?
```{r personnel_cols}
colnames(personnel)
```

```{r duplicates}
nrow(personnel)
nrow(unique(personnel[ ,1:4]))
```

We do not have to worry about duplicate entries.

### Make sure every execid only refers to one person.

```{r check_ids}
personnel %>%
  select(execid, personnel_full_name) %>%
  group_by(execid) %>%
  summarize(n = n_distinct(personnel_full_name)) %>%
  ungroup() %>%
  select(n) %>%
  table(.)
```

It appears all 571 execids all only refer to one person.

### See if individuals changed employees

```{r check_employees}
personnel %>%
  select(execid, gvkey) %>%
  group_by(execid) %>%
  mutate(n = n_distinct(gvkey)) %>%
  # Selecting the first row from each group (individuals) so we can easily see how many employees changed employers out of the total number of tracked individual.
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(n) %>%
  table(.)
```

It seems a few individuals have worked for different employees at different points in time.

## Create personnel exit flag 

```{r }
personnel <- personnel %>%
  group_by(execid, gvkey) %>%
  arrange(execid, year, gvkey) %>%
  mutate(exit = row_number() == n())
```

```{r check_exit}
subset(personnel, execid %in% unique(personnel$execid)[1:3], select = c("gvkey", "name", "execid", "exit"))
```

## Get turnover

### Calculate number of employees tracked each year

```{r n_employees}
personnel <- personnel %>%
  group_by(gvkey, year) %>%
  mutate(n_employees = n())
table(personnel$n_employees)
```

### Calculate how many of the tracked employees exit

```{r exits_total}
personnel <- personnel %>%
  group_by(gvkey, year) %>%
  mutate(n_exits = sum(exit==TRUE)) %>%
  ungroup()
table(personnel$n_exits)
```

### Calculate turnover

```{r turnover}
personnel$turnover <- personnel$n_exits / personnel$n_employees

personnel %>%
  ggplot(aes(x=turnover)) +
  geom_histogram()
```

We notive that we have detected some turnover in top management for many observation. A weakness in our data is that there are also some observations where few top managers are being tracked (or only the CEO is), and hence we get a misleading turnover value of 1. We might want to consider dropping these observationsm, or at least take a closer look.

```{r extreme_values}
nrow(personnel)
nrow(personnel[personnel$turnover == 0, ])
nrow(personnel[personnel$turnover == 1, ])
```

We will look at this data again later, when we have retained only company and year level (and not employee level).

## See CEO change

### Are there years with two CEOs for one company?

```{r ceo_double}
personnel %>%
  filter(personnel_is_ceo == TRUE) %>%
  group_by(gvkey, year) %>%
  mutate(n = n()) %>%
  ungroup() %>%
  select(n) %>%
  table(.)
```

There are not.

### Is there a CEO entry for each company-year observation?

```{r ceo_identified}
personnel %>%
  group_by(gvkey, year) %>%
  # We take advantage of the fact that a TRUE also has an integer value of one in arithmetic operations.
  summarize(ceo_found = max(personnel_is_ceo)) %>%
  ungroup() %>%
  select(ceo_found) %>%
  table(.)
```

Fortunately, the CEO has been identified for every year.

### CEO exit

We can simply use the exit flag for CEOs as an indicator of CEO change.

```{r ceo_exit}
personnel <- personnel %>%
  mutate(ceo_exit = (personnel_is_ceo == TRUE) & (exit == TRUE)) %>%
  group_by(gvkey, year) %>%
  # Again, we take advantage of the fact that a TRUE also has an integer value of one in arithmetic operations.
  mutate(ceo_exit = as.logical(max(ceo_exit))) %>%
  ungroup()
glimpse(personnel)
```

## Convert to company-year

We have obtained all data we wanted from the personnel records. Because we always used group_by operations, all newly generated variables should be constant within every company-year observation.

```{r company-year}
company_year <- unique(select(personnel, gvkey, name, year, n_employees, n_exits, turnover, ceo_exit))

nrow(company_year)

nrow(unique(select(company_year, gvkey, year)))
```

### Plot turnover again

```{r company_turnover}
company_year %>%
  ggplot(aes(x=turnover)) +
  geom_histogram()
```

It looks very similar to the plot we received when plotting by personnel.

### Re-merge recalls
```{r columns}
colnames(recalls_matched)
```

```{r merge}
merge_data <- recalls_matched %>%
  select(gvkey, year, recalls) %>%
  unique()

nrow(merge_data)
nrow(company_year)

company_year <- full_join(company_year, merge_data, by=c("gvkey", "year"))
nrow(company_year)
```

## Save to .feather
```{r save_feather}
feather::write_feather(company_year, paste0("../preprocessed/company_year ", Sys.Date(), ".feather"))
```

## Take a quick look at the results

```{r result}
glimpse(company_year)
```

```{r plot}
company_year %>%
  ggplot(aes(x=turnover, y=recalls)) +
  geom_jitter(alpha=0.15) +
  labs(title = "Turnover vs. Recalls") +
  geom_smooth(method="lm")
```

Let's plot only observations with variance (with nonzero observations of recalls).

```{r plot_variance}
company_year %>%
  group_by(gvkey) %>%
  mutate(n = max(recalls)) %>%
  ungroup() %>%
  filter(n > 0) %>%
    ggplot(aes(x=turnover, y=recalls)) +
    geom_jitter(alpha=0.3) +
    labs(title = "Turnover vs. Recalls (companies with variance only)") +
    geom_smooth(method="lm")
```

```{r plot_loess}
company_year %>%
  ggplot(aes(x=turnover, y=recalls)) +
  geom_jitter(alpha=0.15) +
  labs(title = "Turnover vs. Recalls") +
  geom_smooth(method="loess", color="red")
```

Let's plot only observations with variance (with nonzero observations of recalls).

```{r plot_variance_loess}
company_year %>%
  group_by(gvkey) %>%
  mutate(n = max(recalls)) %>%
  ungroup() %>%
  filter(n > 0) %>%
    ggplot(aes(x=turnover, y=recalls)) +
    geom_jitter(alpha=0.3) +
    labs(title = "Turnover vs. Recalls (companies with variance only)") +
    geom_smooth(method="loess", color="red")
```




