---
title: "9. Exploratory analysis"
author: "Julian Barg"
date: "April 22, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r tidy}
library(tidyverse)
```

## 9.1 Read

```{r read_stata}
library(haven)

pace <- read_stata("../preprocessed/pace 2019-04-22.dta")
glimpse(pace)
```

```{r dtypes}
pace$gvkey <- as_factor(pace$gvkey)
pace$name <- as_factor(pace$name)
pace$ceo_exit <- as.logical(pace$ceo_exit)
pace$ceo_exit_recent <- as.logical(pace$ceo_exit_recent)
pace$ceo_exit_1 <- as.logical(pace$ceo_exit_1)

glimpse(select(pace, gvkey, name, ceo_exit, ceo_exit_recent))
```

## 9.2 Plotting

### 9.2.1 Management team turnover

Turnover only

```{r turnover}
pace %>%
  ggplot(aes(x=turnover_1, y=recalls_change)) +
  geom_jitter() +
  geom_smooth(method="lm")
```

```{r turnover_variance}
pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%  
    ggplot(aes(x=turnover_1, y=recalls_change)) +
    geom_jitter() +
    geom_smooth(method="lm")
```

Turnover-outliers.

```{r pace2}
pace %>%
  ggplot(aes(x=high_turnover_running_3, y=recalls_change)) +
  geom_jitter() +
  geom_smooth(method="lm")

pace %>%
  ggplot(aes(x=high_turnover_running_5, y=recalls_change)) +
  geom_jitter() +
  geom_smooth(method="lm", color="red")
```

```{r pace2_variance}
pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=high_turnover_running_3, y=recalls_change)) +
    geom_jitter() +
    geom_smooth(method="lm")

pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=high_turnover_running_5, y=recalls_change)) +
    geom_jitter() +
    geom_smooth(method="lm", color="red")
```

Turnover elevated

```{r pace}
pace %>%
  ggplot(aes(x=elevated_turnover_running_3, y=recalls_change)) +
  geom_jitter() +
  geom_smooth(method="lm")

pace %>%
  ggplot(aes(x=elevated_turnover_running_5, y=recalls_change)) +
  geom_jitter() +
  geom_smooth(method="lm", color="red")
```

```{r pace_variance}
pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=elevated_turnover_running_3, y=recalls_change)) +
    geom_jitter() +
    geom_smooth(method="lm")

pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=elevated_turnover_running_5, y=recalls_change)) +
    geom_jitter() +
    geom_smooth(method="lm", color="red")
```

### 9.2.2 CEO change

Effective of current year ceo change on current year absolute recalls

```{r ceo_absolute}
pace %>%
  ggplot(aes(x=ceo_exit, y=recalls)) +
  geom_boxplot()

pace %>%
  ggplot(aes(x=ceo_exit_recent, y=recalls)) +
  geom_boxplot()
```

Effective of recent ceo change on current year recalls change

```{r ceo_relative}
pace %>%
  ggplot(aes(x=ceo_exit, y=recalls_change)) +
  geom_boxplot()

pace %>%
  ggplot(aes(x=ceo_exit_recent, y=recalls_change)) +
  geom_boxplot()
```

Effective of recent ceo change on current year recalls change (companies with variance at any point in time only)

```{r ceo_relative_variance}
pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=ceo_exit, y=recalls_change)) +
    geom_boxplot()

pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=ceo_exit_recent, y=recalls_change)) +
    geom_boxplot()

pace %>%
  group_by(gvkey) %>%
  filter(max(recalls, na.rm=TRUE) > 0) %>%
    ggplot(aes(x=ceo_exit_1, y=recalls_change)) +
    geom_boxplot()
```

### 9.2.3 Plotting with residuals

```{r linear model}
model1 <- lm(data = pace, recalls_change ~ growth)
model2 <- lm(data = pace, recalls_change ~ growth_1)
model3 <- lm(data = pace, recalls_change ~ growth + growth_1)
summary(model1)
print("-------------------------------")
summary(model2)
print("-------------------------------")
summary(model3)
```

```{r residuals}
residuals <- model3$residuals
head(residuals)
```

```{r plot_residuals}
pace_residuals <- cbind(pace[!is.na(pace$revenue), ], residuals)

pace_residuals %>%
  ggplot(aes(x=high_turnover_running_3, y=residuals)) +
  geom_point() +
  geom_smooth(method="lm")
```
